Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-25 Grassmannian_cells.tex

\noindent where the $2$-arrows connects the $2$-quiver of $P_{m+1}^{[k]}$ to its Auslander-Reiten translate $\tau P_{m+1}^{[k]}= P_{m-1}^{[k]}$ in $P_m$. This subquiver can be found at the very right of the $2$-quiver of $P_m$. Note that forgo the colouring of the arrows as it does not play any role from the combinatorial point of view. For $n=3$ the $2$-quiver of $P_3$ is given by:\\

@@

The one of $P_4$ is given by:\\

@@

\end{tikzpicture}

\begin{theorem}
  The Euler characteristic $\chi(\Gr_e(P_m^{[k]}))$ is given by the number of strong successor closed subsets of type $e$ of the $2$-quiver of $P_m^{[k]}$.
\end{theorem}
\begin{proof}
  We proceed by induction.
  The strong successor closed subsets of the $2$-quivers of $P_1$, $P_2$ and $P_2^{[n-1]}$ coincide with the successor closed subsets of the coefficient quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{[n-1]}\}$.
  Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\varnothing,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.
  As the number cells of $\Gr_e(\tilde M)$ and $\Gr_e(M)$ coincide, the claim follows.

>>>>

\noindent where the $2$-arrows connects the $2$-quiver of $\tilde P_{m+1}^{[k]}$ to its Auslander-Reiten translate $\tau \tilde P_{m+1}^{[k]}= \tilde P_{m-1}^{[k]}$ in $\tilde P_m$. This subquiver can be found at the very right of the $2$-quiver of $\tilde P_m$. Note that forgo the colouring of the arrows as it does not play any role from the combinatorial point of view. As an example consider the case $n=3$ and $m=3$. The $2$-quiver of $\tilde P_3$ is given by:\\

@@

The one of $\tilde P_4$ is given by:\\

@@

\end{tikzpicture}\\

Write $\mathcal Q(m,k)$ for the $2$-quiver of $\tilde P_m^{[k]}$. Clearly, every vertex  $q\in\mathcal Q(m,k)_0$ corresponds a vertex $\tilde q\in \widetilde{K(n)_0}$. Note that two different vertices of $\mathcal Q(m,k)_0$ can correspond to the same vertex of $\widetilde{K(n)}$. Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset\mathcal Q(m,k)_0$ are defined by
$$\tbfe (\beta)=\sum_{q\in\beta}\tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=F_{K(n)}\tbfe (\beta).$$

\begin{theorem}\begin{enumerate}
\item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$, the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\tbfe $ of the $2$-quiver of $\mathcal Q(m,k)$.
	\item For $\bfe\in\NN^{K(n)_0}$, the Euler characteristic $\chi(\Gr_{\bfe }(P_m^{[k]}))$ is given by the number of strong successor closed subsets of dimension type $\bfe $ of the $2$-quiver of $\mathcal Q(m,k)$.
\end{enumerate}
\end{theorem}
\begin{proof}
The results of Section \ref{QG} imply that the second statement follows from the first one.

We proceed by induction on $m$ and $k$. The strong successor closed subsets of the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$ coincide with the successor closed subsets of the quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{[n-1]}\}$.
  Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\varnothing,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.
  As the number cells of $\Gr_e(\tilde M)$ and $\Gr_e(M)$ coincide, the claim follows.
